The journey of Multiple Sequence Alignment

### 2021-08-03 MSA_Notum_journey.Rmd
pfam hmmscan for WIF seq

```{bash}
hmmsearch --cut_ga --domtblout my_data/hmm_search/NOTUM_profile_domtbl.out my_data/NOTUM_try my_data/pfam/Pfam-A.fasta > /dev/null
```

>>>>

# hmmscan WIF proteins in pfam domains
## export the WIF sequences from oma.db
```{r}
fasta_db_fil_with_len %>% Biostrings::writeXStringSet("WIF_oma_seq.fasta")
```

```{bash}
hmmpress my_data/pfam/Pfam-A.hmm

hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_oma_seq.fasta > /dev/null
